### 2016-01-11 Projects/DelCo_2012/Report/DelCo_2012.tex
update figures, report, plotting scripts

Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking collector bins across the floor surface area of the burn rooms within each structure. The buildings were sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted. Water flowed for a specified duration and upon completion the bins were removed from the structure. Each bin was then weighed to quantify the impact of nozzle location and spray pattern. Thirty-three spray density tests were conducted; 21 were in the burn building and 12 were in the concrete structure. Table~\ref{tab:spray_density_tests} provides an overview of each experiment. In the table, BB stands for the burn building tests while CS stands for the concrete structure tests. For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.

\begin{table}[!ht]
\footnotesize
\centering
\captionof{table}{Spray Density Test Matrix}\label{tab:spray_density_tests}
\begin{tabular}{lllllll}
\toprule[1.5pt]
Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Height (in) & Location (in) \\
\midrule
BB1        &   123              & 15            & Water  &  Solid Stream back  & 20~7/8             &          \\
BB2        &   122              & 23            & Water  &  Solid Stream       &                    &          \\
BB3        &   119              &               & Water  &  Solid Stream       & 16                 &          \\
BB4        &   118              &               & Water  &  Solid Stream       & 16                 &          \\
BB5        &   118              & 20            & Water  &  Solid Stream       & 16                 &          \\
BB6        &   120              & 21            & Water  &  30$^{\circ}$ Fog   & 15                 &          \\
BB7        &   118              & 21            & Water  &  30$^{\circ}$ Fog   & 15                 &          \\
BB8        &   119              & 22            & Water  &  30$^{\circ}$ Fog   & 17                 &          \\
BB9        &   120              & 24            & Water  &  30$^{\circ}$ Fog   & 17~1/2             &          \\
BB10       &   127              & 20            & Water  &  Solid 7/8~in Slug  & 12~1/2             &          \\
BB11       &   120              & 22            & Water  &  Solid 7/8~in Slug  & 11~1/2             &          \\
BB12       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & 12~1/2             &          \\
BB13       &   120 / 60cfm      & 10            & CAF    &  Smooth Bore 7/8~in &                    &          \\
BB14       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in &                    &          \\
BB15       &   120 / 60cfm      & 20            & CAF    &  Smooth Bore 7/8~in &                    &          \\
BB16       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ Fog   & 15                 &          \\
BB17       &   120 / 60cfm      & 20            & CAF    &  Solid Stream narrow & 15                &          \\
BB18       &   120 / 60cfm      & 10            & CAF    &  Solid Stream mid   &                    &          \\
BB19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & 15                 &          \\
BB20       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ Fog   & 17                 &          \\
BB21       &   120 / 60cfm      &               & CAF    &  Solid Stream back  &                    &          \\
CS1        &   115              & 7             & Water  &  Solid Stream       &                    &          \\
CS2        &   115              & 18            & Water  &  Solid Stream       &                    &          \\
CS3        &   120              & 19            & Water  &  Solid Stream       &                    &          \\
CS4        &   118              & 21            & Water  &  Solid Stream       &                    &          \\
CS5        &   118              & 22            & Water  &  30$^{\circ}$ Fog   &                    &          \\
CS6        &   118              & 19            & Water  &  30$^{\circ}$ Fog   &                    &          \\
CS7        &   125              & 16            & Water  &  Solid 7/8~in Slug  &                    &          \\
CS7.2      &   120              & 17            & Water  &  Solid 7/8~in Slug  & 18                 &          \\
CS8        &   116              & 15            & Water  &  30$^{\circ}$ Fog   &                    &          \\
CS9        &   116              & 16            & Water  &  30$^{\circ}$ Fog   &                    &          \\
CS10       &   116              & 16            & Water  &  Solid Stream       &                    &          \\
CS11       &   117              & 16            & Water  &  Solid Stream       &                    &          \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution. Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream positioned {\bf here} the majority of the water accumulated along the north and east walls of the gas cooling room within the burn building (cf. Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}). Figure~\ref{fig:Burn_Building_Test_7} shows difference a fog stream as the distribution of water is far more dispersed around the gas cooling room. The remainder of the burn building spray density figures are included in Appnedix~\ref{app:spray_density}.

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/BB1}
	\caption{Burn Building Test 1}
	\label{fig:Burn_Building_Test_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/BB7}
	\caption{Burn Building Test 7}
	\label{fig:Burn_Building_Test_7}
\end{figure}

@@

The 88 gas cooling experiments were completed as part of 9 separate tests in the burn building. During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 260~$^{\circ}$C (500~$^{\circ}$F). Once this criteria was met, gas cooling began.

>>>>

Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking collector bins across the floor surface area of the burn rooms within each structure. The buildings were sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted. Water flowed for a specified duration and upon completion the bins were removed from the structure. Each bin was then weighed to quantify the impact of nozzle location and spray pattern. Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the concrete structure for the suppression experiments. Tables\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment. In the table, GC stands for the gas cooling experiments while SE stands for the suppression experiments. For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.

For the gas cooling tests, Table~\ref{tab:spray_density_tests}, the mid position had center line of the stream aimed at 2.44~m (8~ft) south of the North wall and 2.13~m (7~ft) west of the East wall in the concrete burn building. The back position had the center line of the stream aimed at 3.36~m (11~ft) south of the North wall and 2.13~m west (7~ft) of the East wall in the concrete burn building.

\begin{table}[!ht]
\footnotesize
\centering
\captionof{table}{Spray Density Test Matrix for Gas Cooling Experiments}\label{tab:spray_density_tests}
\begin{tabular}{llllll}
\toprule[1.5pt]
Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Position  \\
\midrule
GC1        &   123              & 15            & Water  &  Solid Stream       & Back             \\
GC2        &   122              & 23            & Water  &  Solid Stream       & Back             \\
GC3        &   119              & 15            & Water  &  Solid Stream       & Mid              \\
GC4        &   118              & 15            & Water  &  Solid Stream       & Mid              \\
GC5        &   118              & 20            & Water  &  Solid Stream       & Mid              \\
GC6        &   120              & 21            & Water  &  30$^{\circ}$ Fog   & Mid              \\
GC7        &   118              & 20            & Water  &  30$^{\circ}$ Fog   & Mid              \\
GC8        &   119              & 22            & Water  &  30$^{\circ}$ Fog   & Back             \\
GC9        &   120              & 24            & Water  &  30$^{\circ}$ Fog   & Back             \\
GC10       &   127              & 20            & Water  &  Solid 7/8~in Slug  & Back             \\
GC11       &   120              & 22            & Water  &  Solid 7/8~in Slug  & Back             \\
GC12       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & Back             \\
GC13       &   120 / 60cfm      & 10            & CAF    &  Smooth Bore 7/8~in & Mid              \\
GC14       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & Back             \\
GC15       &   120 / 60cfm      & 20            & CAF    &  Smooth Bore 7/8~in & Mid              \\
GC16       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Mid              \\
GC17       &   120 / 60cfm      & 20            & CAF    &  Solid Stream       & Mid             \\
GC18       &   120 / 60cfm      & 10            & CAF    &  Solid Stream       & Mid             \\
GC19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
GC20       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
GC21       &   120 / 60cfm      & 15            & CAF    &  Solid Stream       & Back             \\

\bottomrule[1.25pt]
\end{tabular}\par
\end{table}
For the fire suppression spray density experiments, Table~\ref{tab:spray_density_tests2}, the hallway position had the center of the stream aimed at the ceiling of the burn room, 2.14~m (7~ft) north of the South wall and 1.53~m (5~ft) east of the West wall. The fire room position had the center of the stream aimed at the ceiling of the burn room, 2.14~m (7~ft) north of the South wall and 3.05~m (10~ft) west of the East wall.

\begin{table}[!ht]
\footnotesize
\centering
\captionof{table}{Spray Density Test Matrix for Fire Suppression Experiments}\label{tab:spray_density_tests2}
\begin{tabular}{llllll}
\toprule[1.5pt]
Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Location  \\
\midrule
SE1        &   115              & 7             & Water  &  Solid Stream       &    Fire Room          \\
SE2        &   115              & 18            & Water  &  Solid Stream       &    Fire Room          \\
SE3        &   120              & 19            & Water  &  Solid Stream       &    Fire Room          \\
SE4        &   118              & 21            & Water  &  Solid Stream       &    Fire Room          \\
SE5        &   118              & 22            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
SE6        &   118              & 19            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
SE7        &   125              & 16            & Water  &  Solid 7/8~in Slug  &    Fire Room          \\
SE8        &   120              & 17            & Water  &  Solid 7/8~in Slug  &    Hallway            \\
SE9        &   116              & 15            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
SE10       &   116              & 16            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
SE11       &   116              & 16            & Water  &  Solid Stream       &    Hallway            \\
SE12       &   117              & 16            & Water  &  Solid Stream       &    Hallway            \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution. Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream in the back position, the majority of the water accumulated along the North and East walls of the gas cooling room within the burn building (cf. Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}). Figure~\ref{fig:Burn_Building_Test_7} shows difference a fog stream as the distribution of water is far more dispersed around the gas cooling room. The remainder of the burn building spray density figures are included in Appnedix~\ref{app:spray_density}.

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/BB1}
	\caption{Gas Cooling Spray Density Test 1}
	\label{fig:Burn_Building_Test_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Bars/BB7}
	\caption{Gas Cooling Spray Density Test 7}
	\label{fig:Burn_Building_Test_7}
\end{figure}

@@

The 88 gas cooling experiments were completed as part of 9 separate tests in the burn building. During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F). Once this criteria was met, gas cooling began.
